\begin{thebibliography}{00}
	\bibitem{b1} Aggarwal, K. K., et al. "Investigating effect of Design Metrics on Fault Proneness in Object-Oriented Systems." J. Object Technol. 6.10 (2007): 127-141.
	\bibitem{b2} Aggarwal, K. K., et al. "Empirical analysis for investigating the effect of object‐oriented metrics on fault proneness: a replicated case study." Software process: Improvement and practice 14.1 (2009): 39-62.
	\bibitem{b3} Al Dallal, Jehad. "Fault prediction and the discriminative powers of connectivity-based object-oriented class cohesion metrics." Information and Software Technology 54.4 (2012): 396-416.
	\bibitem{b4} Al Dallal, Jehad. "The impact of accounting for special methods in the measurement of object-oriented class cohesion on refactoring and fault prediction activities." Journal of Systems and Software 85.5 (2012): 1042-1057.
	\bibitem{b5} Bellini, Pierfrancesco, et al. "Comparing fault-proneness estimation models." 10th IEEE International Conference on Engineering of Complex Computer Systems (ICECCS'05). IEEE, 2005.
	\bibitem{b6} Aggarwal, K. K., et al. "Investigating effect of Design Metrics on Fault Proneness in Object-Oriented Systems." J. Object Technol. 6.10 (2007): 127-141.
	\bibitem{b7} Radjenovic, Danijel et al. “Software fault prediction metrics: A systematic literature review.” Inf. Softw. Technol. 55 (2013): 1397-1418.
	\bibitem{b8}Dallal, Jehad Al and L. Briand. “A Precise Method-Method Interaction-Based Cohesion Metric for Object-Oriented Classes.” ACM Trans. Softw. Eng. Methodol. 21 (2012): 8:1-8:34.
	\bibitem{b9} G. J. Pai and J. Bechta Dugan, "Empirical Analysis of Software Fault Content and Fault Proneness Using Bayesian Methods," in IEEE Transactions on Software Engineering, vol. 33, no. 10, pp. 675-686, Oct. 2007, doi: 10.1109/TSE.2007.70722.
	\bibitem{b10} El Emam, Khaled, Walcelio Melo, and Javam C. Machado. "The prediction of faulty classes using object-oriented design metrics." Journal of systems and software 56.1 (2001): 63-75.
	\bibitem{b11} Basili, Victor R., Lionel C. Briand, and Walcélio L. Melo. "A validation of object-oriented design metrics as quality indicators." IEEE Transactions on software engineering 22.10 (1996): 751-761.
	\bibitem{b12} Briand, Lionel C., Walcelio L. Melo, and Jurgen Wust. "Assessing the applicability of fault-proneness models across object-oriented software projects." IEEE transactions on Software Engineering 28.7 (2002): 706-720.
	\bibitem{b13} Singh, Yogesh, Arvinder Kaur, and Ruchika Malhotra. "Empirical validation of object-oriented metrics for predicting fault proneness models." Software quality journal 18.1 (2010): 3.
	\bibitem{b14} Chidamber, Shyam R., and Chris F. Kemerer. "A metrics suite for object oriented design." IEEE Transactions on software engineering 20.6 (1994): 476-493.
	\bibitem{b15} Chidamber, Shyam R., and Chris F. Kemerer. "Towards a metrics suite for object oriented design." Conference proceedings on Object-oriented programming systems, languages, and applications. 1991.
\end{thebibliography}